The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
tidy + setup hab sel

## Habitat selection and space use
Animals use space for resource, considering conspecifics

social structure is influenced by resources

animals selectively use resources + can be measured by RSFs

<!-- Social structure influenced by large scale processes, eg resources -->
<!-- Animals select for these same processes, habitat selection, as measured by RSF -->
<!-- All of these processes are influenced by scale:  -->
<!-- RSFs are are influenced -->
<!-- Habitat selection johnsons four orders Mayor 2009, scale can be explicitly considered -->
<!-- sociality across scales of sociality + temporal and spatial as shown above -->
<!-- ML networks present a framework for this -->

<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999]. Combined,
social structure and habitat selection are intimately linked as individuals must
share space to interact and the distribution of resources influences home range size
and group dynamics [@Webber_2018].

Habitat selection is a scale-sensitive process
Animals select habitats at multiple scales

<!-- Mayor scale --> Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.

Johnson
(1980) identified four orders of habitat selection: (1) the geographical range
of a species, (2) the home range of an individual, (3) the habitat patches
within the home range and (4) specific resources within a habitat patch.

<!--
* multilayer networks are new but folks have looked at habitat selection + sociality
  * Fortin
  * Banks
  * McLoughlin

* none use a multilayer framework to explicitly combine
-->

@@

@@

* Mayor et al. 2009 paper 
* MRSF Laforge paper 
* van Beest et al. 2014 scale paper 
* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
* Multi-scale habitat selection modeling: a review and outlook
-->
Scale in habitat selection... Mayor (2019)

>>>>

## Habitat selection and space use
<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999].
Combined, social structure and habitat selection are intimately linked as
individuals must share space to interact and the distribution of resources
influences home range size and group dynamics [@Webber_2018]. Animals select
habitats are multiple scales ... (Mayor) <!-- Mayor scale --> Multilayer
networks represent a novel framework for considering the influence of habitat
selection and space use on sociality across scales.

<!-- Relationship between sociality and habitat -->
<!-- more from Webber, He, etc -->
<!-- Merkle’s memory and patches for bison (and leaders) -->
<!-- Emergent  Properties  of  Conspecific  Attraction  inFragmented  Landscapes-->
<!-- Conspecific Attraction and Aggregation in Territorial Species-->
<!-- Energy and the Scaling of Animal Space Use-->

<!-- The relationship between sociality has been discussed both theoretically  -->
<!-- and tested explicitly ... CAH, etc then Fortin, McLouglin-->
<!-- https://www.pnas.org/content/pnas/105/49/19114.full.pdf
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2600907/pdf/rspb20071688.pdf
-->

@@

Habitat selection - can be measured by RSFs and importance of scale:

*  Johnson (1980) identified four orders of habitat selection: (1) the geographical range of a species, (2) the home range of an individual, (3) the habitat patches within the home range and (4) specific resources within a habitat patch.

What new insights will multilayer networks lead to

@@

* Mayor et al. 2009 paper 
* MRSF Laforge paper 
* van Beest et al. 2014 scale paper 
* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
* Multi-scale habitat selection modeling: a review and outlook
-->

Scale in habitat selection... Mayor (2019)
